Bayesian statistics and swine flu

### 2009-05-11 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@294 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}[fragile]
\frametitle{What we need}
\begin{verbatim}
transition parameter mean sd distribution
InfOns	mean	1	1	gamma	
InfOns	shape	1	1	gamma	
InfOns	zeros	0.1	0.1	beta	
OnsMedM	mean	1	1	gamma	
OnsMedM	shape	1	1	gamma	
OnsMedM	zeros	0.1	0.1	beta	
OnsMedS	mean	1	1	gamma	
OnsMedS	shape	1	1	gamma	
OnsMedS	zeros	0.1	0.1	beta	
OnsMedD	mean	1	1	gamma	
OnsMedD	shape	1	1	gamma	
OnsMedD	zeros	0.1	0.1	beta	
\end{verbatim}
\end{frame}

\begin{frame}
\frametitle{Prior graphs}
<<priorGraph, fig=false,results=tex>>=
priors= pandemicPriors()
plotPrior(priors$InfOns, file="InfOns", tex=TRUE)
@
\end{frame}

\begin{frame}
\frametitle{Inference}

@@

\begin{frame}
\frametitle{Simulated data}

>>>>

\begin{frame}[fragile]
\frametitle{What we need}
\begin{verbatim}
transition parameter mean sd distribution
InfOns	mean	1	1	gamma	
InfOns	shape	1	1	gamma	
InfOns	zeros	0.1	0.1	beta	
OnsMedM	mean	1	1	gamma	
OnsMedM	shape	1	1	gamma	
OnsMedM	zeros	0.1	0.1	beta	
OnsMedS	mean	1	1	gamma	
OnsMedS	shape	1	1	gamma	
OnsMedS	zeros	0.1	0.1	beta	
OnsMedD	mean	1	1	gamma	
OnsMedD	shape	1	1	gamma	
OnsMedD	zeros	0.1	0.1	beta	
MedRec	mean	1	1	gamma	
MedRec	shape	1	1	gamma	
MedRec	zeros	0.1	0.1	beta	
MedRec	lost	1	1	beta	
\end{verbatim}
\end{frame}

\begin{frame}
\frametitle{Prior graphs}
<<priorGraph, fig=false,results=tex>>=
priors= pandemicPriors()
plotPrior(priors$InfOns, file="InfOns", tex=TRUE)
#$
@

@@

\begin{frame}
\frametitle{Inference}
\begin{itemize}
	\item We have data $Y$ and unknown parameters $\theta$.
	\item The model specifies $[Y|\theta]$
	\item Priors are $[\theta]$.
	\item Posteriors: $[\theta|Y] \propto [Y|\theta][\theta]$
	\item Posteriors show what we think the parameters could be, given the data and the prior distributions
	\item There's no data on infection times, so the posterior for $\mu_{I}$ is the same as the prior.
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Simulated data}
<<simData,echo=true,fig=false>>=
params = pandemicParams()
 data = simEpidemic(params, 30)
@
\end{frame}

\begin{frame}
\frametitle{Simulated data}
<<simDataTable,results=tex,fig=false>>=
toPrint = data[1:12,]
toPrint[is.na(toPrint)] = " "
toPrint = as.matrix(toPrint)
latex(toPrint, file="",center="none", title="", table.env=F)
@
\end{frame}
